---
title: "Example mlr3 analysis"
subtitle: "Disease classification in Indian Liver Patient Dataset"
date: "`r format(Sys.time(), '%d %B %Y')`"
author: Paul Yousefi
output:
  html_document:
    css: docs/style.css
    toc: true
    highlight: tango
---

```{r setoptions, eval = TRUE, echo = FALSE}
knitr::opts_chunk$set(
comment = ">",
error = FALSE,
tidy = FALSE,
echo = TRUE, 
warning = FALSE, 
message = FALSE,
cache=FALSE)
```

```{r call_source, echo = F}
path <- "."
sourcecode <- grep("analysis.r$", 
	list.files(path), value = T)
read_chunk(file.path(path, sourcecode))
```

# Indian Liver Patient Dataset

The Indian Liver Patient Dataset is an epidemiological dataset distributed freely through `mlr3`, details available here: https://mlr3data.mlr-org.com/reference/ilpd.html 


```{r globals, results = 'hide'}
```

## Load the data

```{r load.data}
```

## Prep the data for machine learning

Convert binary variables coded as factors, `gender` and `diseased`, to be 'logic' variables (i.e. `TRUE`/`FALSE`) that `mlr3` can accommodate

```{r prep.data}
```

# Define the claffication task 

Set the machine learning task in `mlr3` syntax:
```{r task}
```

Split the task to reserve 20% of the the data as fully independent test data

```{r split}
```

# Specify the library of pipelines for performing the classification task

Define individual pipelines of machine learning alogorithms for performing the prediction task we have set.

This set of pipelines will make of the library of learning approaches that we'll compare for performing our classification task. 

Each pipeline has a name (e.g. `rf`, `xgboost`, etc.) that we'll use to refer to when defining our library.


```{r rf}
```

```{r lasso}
```

```{r elasticnet}
```

```{r xgboost}
```

# Apply each pipeline to the classication task

We now apply each pipeline in the library to the classifiction task in a fair comparison where each has access to the same training and testing observations

```{r bm, results = 'hide'}
```

# Calculate and summarise the performance of each pipeline 

```{r metrics}
```

```{r plots}
```
